---
title: "IB 120/201 - Homework 10"
author: 'GSI: Ksenia Arzumanova'
date: 'Due: April 9, 2021 by 12:59pm PST'
output:
  html_document: default
  pdf_document: default
subtitle: Bootstrapping
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Question 1
Load the `iris` dataset, and find the mean and SEM of the `Sepal.Length`, `Sepal.Width`, `Petal.Length`, `Petal.Width`.

```{r q1}
meanSepLen <- NULL
meanSepWid <- NULL
meanPetLen <- NULL
meanPetWid <- NULL

semSepLen <- NULL
semSepWid <- NULL
semPetLen <- NULL
semPetWid <- NULL
```

### Question 2
Calculate the variance of `Sepal.Length`, `Sepal.Width`, `Petal.Length`, `Petal.Width`.

```{r q2}
varSepLen <- NULL
varSepWid <- NULL
varPetLen <- NULL
varPetWid <- NULL
```

### Question 3
Using the values calculated above, obtain the 95% confidence interval of the mean for `Sepal.Length`, `Sepal.Width`, `Petal.Length`, `Petal.Width`. What determines the range of the confidence interval? Report the confidence interval as a vector of the lower and upper bounds : `c(lower bound of CI, upper bound of CI)`.

```{r q3}
sepLenCI <- NULL
sepWidCI <- NULL
petLenCI <- NULL
petWidCI <- NULL
```

### Question 4
Obtain 500 bootstrap samples out of `Sepal.Length`, `Sepal.Width`, `Petal.Length`, `Petal.Width`:
(a) Create a histogram of the bootstrap sample means
(b) Find the 95% bootstrap confidence intervals

```{r q4}

```

### Question 5
Perform a t-test between all combinations of the four datasets (that would be a total of 4 choose 2 = 6 combinations). See if there is any statistically significant difference (p < 0.05) between any of the four parameters defining the `iris`. 

```{r q5}

```




